\chapter{Abstract}
Option is the most popluer derivetive trading in market. 
%So evaluate the value of options is
%a very important question in finicial industry.
%However the return of options can only be determined when it is exercised.
%So option pricing became a very difficult problem.
In the most important model, Black-Schore model, for option princing, 
the price of underling asset is assumed to 
satisfy the geometric Brownian motion, 
which is a very interesting object itself. 
We will have a quick review about the theory of option pricing
in the fist part of this thesis.
%So option priceing is a  very interesting and important problem
%both in practical and theratical. 
It is well know that Black-Schore formula solve pricing problem 
for European option.
However for other types of options, usually there is no such nice formula. 
Numerical methods are developed to solve these problems. 
In this article, we are consider the $\alpha$-quantile options. 
Partially because the $\alpha$-quantiles of Brownian motion 
are highly path-dependent, 
there still many fundamental problems are open now.
One problem is the discrete error between the $\alpha$-quantile 
of Brownian motion and Gaussian random walk. 
This is the first step to find the approximation order of numerical 
methods based on Gaussian random walk.
We have find a very different 
convergence pattern of the discrete error for genuine $\alpha$-quantiles
and the maximal($\alpha=1$) by simulation. 
Moreover we show these differences theoretically.
Another problem is using tree methods to pricing 
$\alpha$-quantile options. We will discuss two different approchs for pricing
European type $\alpha$-quantile options.
Although the second method is non efficency, 
it propose a method to deal American type $\alpha$-quantile options. 
Enlightening by the results of the convergence pattern,
we considered methods accelerateing the convergence rate by Richardson extrpolation.  
\vspace{1cm}

\noindent{\bf Keywords}: Option Pricing, $\alpha$-quantile Options, Discrete error, Tree Methord, Lattice Method, American option, Optimal Stopping Problem, Richardson extropolation
